Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis.tex
updated plots

\begin{figure*}
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[scale=.4]{figures/types_instances.png}
\end{minipage}
\begin{minipage}[b]{0.6\linewidth}
\includegraphics[scale=.4]{figures/types_classes.png}
\end{minipage}
 \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, based on different frequency tresholds (applied on the level of instances and classes respectively)}
\end{figure*}

@@

\begin{tabular}{lccccc|ccccc}
\toprule
 & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
\midrule
            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
            \midrule
                     people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
                 buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
                  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
 animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
\bottomrule
\end{tabular}

\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vg synset), for filtered response sets (frequency threshold of 2)}
\label{tab:agree}
\end{table*}

@@

\begin{description}[style=unboxed,leftmargin=0.2cm]
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
%\setlength{\leftmargin}{0pt}
\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box. They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}). Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
\item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
\item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}). 
\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
\end{description}

>>>>

\begin{figure*}
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[scale=.4]{figures/types_instances.png}
\end{minipage}
\begin{minipage}[b]{0.6\linewidth}
\includegraphics[scale=.4]{figures/types_classes.png}
\end{minipage}
\vspace{-0.8cm}
 \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, with frequency thresholds}
\end{figure*}

@@

\begin{tabular}{lccccc|ccccc}
\toprule
 & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
\midrule
            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
            \midrule
                     people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
                 buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
                  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
 animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
\bottomrule
\end{tabular}
\vspace{-0.3cm}
\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vg synset), for filtered response sets (frequency threshold of 2)}
\label{tab:agree}
\end{table*}

@@

%\vspace{-0.5cm}
\begin{description}[style=unboxed,leftmargin=0.2cm]
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
%\setlength{\leftmargin}{0pt}
\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box. They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}). Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
\item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
\item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}). 
\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
\end{description}
\vspace{-0.2cm}
